SDR enhancement by clouds

### 2024-03-20 article/article.Rmd
Commit 2024-03-20 23:09

In this study, we evaluated the effects of the clouds on th

@@

The recording of the signal is the one-minute average.
Thus, we will refer to this timescale as a cloud enhancement event (CE).

@@

After some evaluation of the modeled radiation in different atmospheric conditions,
in relation to the GHI data, we choose as representative of the clear sky radiation,
the case with
$t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.

Which is an expected result as these values represent a typical atmosphere in
Thessaloniki with low load of aerosols and humidity, which are the main factor that
attenuate the GHI, excluding clouds.

@@

Criteria for cloud enhancement identification are set according the Equation \ref{eq:CE4}

\begin{equation}
\text{CE}_\text{Threshold} = \begin{cases}
`r C4_cs_ref_ratio`, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4}
\end{equation}
where: $\theta$ solar zenith angle.

A secondary criterion was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})

\begin{equation}
\text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
\label{eq:ECE}
\end{equation}

@@

<!-- todo stop long tails on hist -->
<!-- hist retative frequency label -->

<!-- Whisky plot relative between months -->
<!-- weight (Nmonth / Nmaxmonth) -->

@@

Another aspect of the CE events are the cases where the irradiance is above the expected irradiance on top of the atmosphere, we have defined this

```{r echo=FALSE, fig.cap="Distribution of "}
knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")
```

@@

-   max value ECE
-   seasonal
-   trends
-   duration
-   occurrence
-   SZA

## New plots for discussion

>>>>

In this study, we evaluated the effects of the clouds on the total downward radiation
by studding the occurrences of the cloud enhancement cases, their intensity and their
duration.  The recording of the radiation signal is the one-minute average.  Thus, we
will refer to this time step as a cloud enhancement event (CE).

@@

@@

After some evaluation of the modeled radiation in different atmospheric conditions,
in relation to the GHI data, we choose as a representative of the clear sky radiation,
the case with
$t_{\text{cs}} = t_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$.

These values will represent a typical atmosphere in
Thessaloniki with low load of aerosols and humidity, which are the main factor that
attenuate the GHI, excluding clouds.
We will refer to this irradiance as $\text{GHI}_\text{mCSi}$.

@@

Criteria for cloud enhancement identification are set according the Equation\nobreakspace\ref{eq:CE4}

<!--
\begin{equation}
\text{CE}_\text{Threshold} = \begin{cases}
`r C4_cs_ref_ratio`, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4}
\end{equation}
where: $\theta$ solar zenith angle.
-->

\begin{equation}
\text{CE} : \begin{cases}
 \text{GHI}_\text{i} > `r C4_cs_ref_ratio` \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq `r C4_lowcut_sza`^\circ$}\\
\text{GHI}_\text{i} > \left ({ `r C4_lowcut_ratio` + \frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}\\
\text{Excluded measurements}, & \theta > `r 90 - BIO_ELEVA`^\circ
\end{cases}\label{eq:CE4b}
\end{equation}
where: $\theta$ solar zenith angle.

A secondary criterion was used for extreme cloud enhancement cases (ECE)
identification, relative to the TSI at horizontal plane
(Equation\nobreakspace{}\ref{eq:ECE})

\begin{equation}
\text{ECE}: \text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
\label{eq:ECE}
\end{equation}

@@

@@

Another aspect of the CE events are the cases when the irradiance is above the
expected irradiance on top of the atmosphere, we have defined this as ECE
(Equation\nobreakspace{}\ref{eq:ECE}).

-  max value ECE
  relative to other works max values

Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies} we have
computed the distribution of the number of occurrences of ECE events by month in
Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the most active
period is in the spring (March -- May), followed by the months of June, September and
October.

.......

```{r relative-month-occurancies-ECE, echo=FALSE, fig.cap="Distribution of "}
knitr::include_graphics("../images/clim_ECE_month_norm_MAX_median_N-2.png")
```

@@

-   SZA

### 2024-03-20 article/article.tex
Commit 2024-03-20 23:09

After some evaluation of the modeled radiation in different atmospheric conditions,
in relation to the GHI data, we choose as representative of the clear sky radiation,
the case with
\(t_{\text{cs}} = t_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\).

Which is an expected result as these values represent a typical atmosphere in
Thessaloniki with low load of aerosols and humidity, which are the main factor that
attenuate the GHI, excluding clouds.

@@

Criteria for cloud enhancement identification are set according the Equation \ref{eq:CE4}

\begin{equation}
\text{CE}_\text{Threshold} = \begin{cases}
1.05, & \text{$\theta \leq 60^\circ$}\\
\frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) + 1.18 , & \text{$ 78^\circ > \theta > 60^\circ$}\\
\text{Excluded measurements}, & \theta > 78^\circ
\end{cases}\label{eq:CE4}
\end{equation}
where: \(\theta\) solar zenith angle.

A secondary criterion was used for extreme cloud enhancement cases (ECE) identification, relative to the TSI at horizontal plane (Equation \ref{eq:ECE})

\begin{equation}
\text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
\label{eq:ECE}
\end{equation}

@@

Another aspect of the CE events are the cases where the irradiance is above the expected irradiance on top of the atmosphere, we have defined this

@@

\caption{Distribution of }\label{fig:unnamed-chunk-4}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-5}
\end{figure}

\begin{itemize}
\tightlist
\item
  max value ECE
\item
  seasonal
\item
  trends
\item
  duration
\item
  occurrence
\item
  SZA
\end{itemize}

\hypertarget{new-plots-for-discussion}{%
\subsection{New plots for discussion}\label{new-plots-for-discussion}}

>>>>

After some evaluation of the modeled radiation in different atmospheric conditions,
in relation to the GHI data, we choose as a representative of the clear sky radiation,
the case with
\(t_{\text{cs}} = t_{500\text{nm}} - 1\sigma\) and \(w_{h\text{cs}} = w_h - 1\sigma\).

These values will represent a typical atmosphere in
Thessaloniki with low load of aerosols and humidity, which are the main factor that
attenuate the GHI, excluding clouds.
We will refer to this irradiance as \(\text{GHI}_\text{mCSi}\).

@@

Criteria for cloud enhancement identification are set according the Equation\nobreakspace\ref{eq:CE4}

\begin{equation}
\text{CE} : \begin{cases}
 \text{GHI}_\text{i} > 1.05 \cdot \text{GHI}_\text{mCSi}, & \text{$\theta \leq 60^\circ$}\\
\text{GHI}_\text{i} > \left ({ 1.18 + \frac{1.05 - 1.18}{60 - 78} \cdot (\theta- 78) } \right ) \cdot \text{GHI}_\text{mCSi}, & \text{$ 78^\circ > \theta > 60^\circ$}\\
\text{Excluded measurements}, & \theta > 78^\circ
\end{cases}\label{eq:CE4b}
\end{equation}
where: \(\theta\) solar zenith angle.

A secondary criterion was used for extreme cloud enhancement cases (ECE)
identification, relative to the TSI at horizontal plane
(Equation\nobreakspace{}\ref{eq:ECE})

\begin{equation}
\text{ECE}: \text{GHI} > \cos(\theta) \times \text{TSI}_\text{TOA}
\label{eq:ECE}
\end{equation}

@@

Another aspect of the CE events are the cases when the irradiance is above the
expected irradiance on top of the atmosphere, we have defined this as ECE
(Equation\nobreakspace{}\ref{eq:ECE}).

\begin{itemize}
\tightlist
\item
  max value ECE
  relative to other works max values
\end{itemize}

Analogous to Figure\nobreakspace{}\ref{fig:relative-month-occurancies} we have
computed the distribution of the number of occurrences of ECE events by month in
Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. Here the most active
period is in the spring (March -- May), followed by the months of June, September and
October.

\ldots\ldots.

@@

\caption{Distribution of }\label{fig:relative-month-occurancies-ECE}
\end{figure}

@@

\caption{Distribution of ECE above 'clear sky' reference}\label{fig:unnamed-chunk-4}
\end{figure}

\begin{itemize}
\tightlist
\item
  SZA
\end{itemize}
